---
output: github_document
editor_options: 
  chunk_output_type: inline
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# netdiagnostics

![](badges/lifecycle-experimental-orange.svg) ![](badges/license-MIT-blue.svg)

The goal of `netdiagnostics` is to combine multiple test results to form an equivalent single test with respect to sensitivity and specificity.

## Installation

You can install the development version from [GitHub](https://github.com/n8thangreen/netdiagnostics) with:

``` r
# install.packages("devtools")
devtools::install_github("n8thangreen/netdiagnostics")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(netdiagnostics)
net_sensspec(pos_threshold = 2,
             sens = c(0.1,0.2,0.3,0.4),
             spec = c(0.1,0.2,0.3,0.4))
```

