---
title: "netdiagnostics"
author: "Nathan Green"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

This package is designed to:

- take multiple tests, completely defined by their unique sensitivity and specificity
- combine their test results determined by a minimum number of positives required for an overall _net_ performance
- give this net sensitivity and specificity as if it were a single test

## Worked example


### Intuition

Below is a Venn diagram representing the multiple tests and their combinations of test results:

```{r, echo=FALSE, warning=FALSE, warning=F, fig.width=5, fig.height=5}
library(VennDiagram, quietly = T, verbose = F)

venn.plot <- draw.triple.venn(
	area1 = 65,
	area2 = 75,
	area3 = 85,
	n12 = 35,
	n23 = 15,
	n13 = 25,
	n123 = 5,
	category = c("Test 1", "Test 2", "Test 3"),
	fill = c("blue", "red", "green"),
	lty = "blank",
	cex = 2,
	cat.cex = 2,
	cat.col = c("blue", "red", "green"))

grid.draw(venn.plot)

```


### forumulae

The maths is $Y = X\beta + \epsilon$, footnotes^[A footnote here.],

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```


